\documentclass[12pt]{article}
\pdfoutput=1

\usepackage{hyperref}
\usepackage[margin=3cm]{geometry}
\usepackage[backend=biber,sorting=ynt]{biblatex}
\addbibresource{references.bib}

\begin{document}

\title{My \LaTeX-ed references}
\author{
	Llu\'is Alemany-Puig
}

\maketitle

Citations:
\begin{enumerate}
	\item[\cite{Alemany2019a}] L. Alemany-Puig. ``{\em Edge crossings in linear arrangements: from theory to algorithms and applications}''. In: {\em Universitat Politècnica de Catalunya}. Handle: \url{http://hdl.handle.net/2117/168124}.
	
	\item[\cite{Alemany2020a}] L. Alemany-Puig and R. Ferrer-i-Cancho. ``{\em Edge crossings in random linear arrangements}''. In: {\em Journal of Statistical Mechanics: Theory and Experiment} 2020.2 (Feb 2020) p. 023403. \textsc{Doi}: \url{https://doi.org/10.1088/1742-5468/ab6845}.

	\item[\cite{Alemany2020b}] L. Alemany-Puig and M. Mora and R. Ferrer-i-Cancho. ``{\em Reappraising the distribution of the number of edge crossings of graphs on a sphere}''. In: {\em Journal of Statistical Mechanics: Theory and Experiment} 2020.8 (Aug 2020) p. 023403. \textsc{Doi}: \url{http://doi.org/10.1088/1742-5468/aba0ab}.

	\item[\cite{Alemany2020c}] L. Alemany-Puig and R. Ferrer-i-Cancho. ``{\em Fast calculation of the variance of edge crossings in random linear arrangements}''. In: {\em arXiv} (2020). arXiv: 2003.03258. URL: \url{http://arxiv.org/abs/2003.03258}.
	
	\item[\cite{Ferrer2020a}] R. Ferrer-i-Cancho and G{\'{o}}mez-Rodr{\'{i}}guez, Carlos and J. L. Esteban and L. Alemany-Puig. ``{\em The optimality of syntactic dependency distances}''. In: {\em arXiv} (2020). arXiv: 2007.15342. URL: \url{http://arxiv.org/abs/2007.15342}.
	
	\item[\cite{Ferrer2020a}] L. Alemany-Puig and J. L. Esteban and R. Ferrer-i-Cancho. ``{\em Minimum projective linearization of trees in linear time}''. In: {\em arXiv} (2020). arXiv: 2102.03277. URL: \url{http://arxiv.org/abs/2102.03277}.
	
\end{enumerate}

\printbibliography

\end{document}

